Rotation effects on the Lyman-$\alpha$ line morphology in distant galaxies

### 2013-05-15 paper/Analisis.tex
Nscatt Histograms, Homogeneous & Central
Average Num. of Scatt Section

As a first approach we study the number of scatterings of all the photons at different velocites and for both distributions Figure~\ref{fig:Nscatt}. For the central distribution we found that the average number of scattering does not have a relevant change (put the exact value) with $V_{max}$, For the Homogeneous distribution we found that as $V_{max}$ increase the average number of scatterings decrease, it means that rotation make photons to escape easier from the cloud, and the reason why this is not observed in the central distribution. it is because the amount of gas that every photon has to break through is so large an so the average number of scatterings, making the effect of rotation unobservable.

In order to understand the morphology of the line we make a histogram of $<N_{scatt}>$  in function of $X_{m}$

as we think Nscatt is related with the double peacked line and maxima positions.

@@

\begin{figure*}
    \includegraphics[width=0.45\textwidth]{2dHistogram50Central5t.png}
    \includegraphics[width=0.45\textwidth]{2dHistogram300Central5t.png}
\caption{Histogram of $N_{scatt}$ vs $X_{m}$ for the central distribution\label{fig:NscattHisto}} 
\end{figure*}

\begin{figure*}
    \includegraphics[width=0.45\textwidth]{2dHistogramt5HOM.png}
    \caption{Histogram of $N_{scatt}$ vs $X_{m}$ for the homogeneous distribution\label{fig:NscattHistoHOM}} 
\end{figure*}

>>>>

As a first approach we study the number of scatterings of all the photons at different velocites and for both distributions Figure~\ref{fig:Nscatt}. For the central distribution we found that the average number of scattering does not have a relevant change (put the exact value) with $V_{max}$, For the Homogeneous distribution we found that as $V_{max}$ increase the average number of scatterings decrease, it means that rotation make photons to escape easier from the cloud, and the reason why this is not observed in the central distribution. it is because the amount of gas that every photon has to break through is so large an so the average number of scatterings, making the effect of rotation unobservable.\\

In order to understand the effects of rotation in the morphology of the line we make histograms of $<N_{scatt}>$  in function of $X_{m}$ for both the central Fig. ~\ref{fig:NscattHisto} and the  homogeneous distribution Fig.~\ref{fig:NscattHistoHOM}. For the central distribution and for lower velocities we found that for some value (put the value) of $N_{scatt}$ the mayority of photons have a defined value of $X_{m}$. While for higher velocities photons tend spread out in $X_{m}$(Make position analysis of this photons).\\

For the homogenepus distribution we found the same effect but also, for highest velocities the mayority of the photons near the surface escape with much less scatterings that in the static case. This analysis let us conclude that rotation make photons escape with less scatterings and it spread out the wavelenght of the of the outgoing photons represented by $X_{m}$.

@@

\begin{figure*}
    \includegraphics[width=0.54\textwidth]{test4.png}%this is the central}
\caption{Histogram of $N_{scatt}$ vs $X_{m}$ for the central distribution\label{fig:NscattHisto}} 
\end{figure*}

\begin{figure*}
     \includegraphics[width=0.54\textwidth]{test3.png}%this is the homogeneous

    \caption{Histogram of $N_{scatt}$ vs $X_{m}$ for the homogeneous distribution\label{fig:NscattHistoHOM}} 
\end{figure*}
